---
title: "R Notebook"
output: html_notebook
---
Packages
```{r}
library(haven)
library(ggplot2)
library(dplyr)
library(gt)
```

Import
```{r}
adae <- read_sas("https://github.com/elong0527/r4csr/raw/master/data-adam/adae.sas7bdat", 
    NULL)
View(adae) #This is to view the adae dataset in a new window
adae #This is to open adae in Rmarkdown as below
```

Prep data
```{r}

library(dplyr)
library(ggplot2)

adae %>%
 filter(!(AEREL %in% "")) %>%
 ggplot() +
 aes(x = AEREL, fill = TRTA) +
 geom_bar() +
 scale_fill_hue(direction = 1) +
 theme_minimal()

```




Prep Data
```{r}
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
```{r}

```

