---
title: "R Notebook"
output: html_notebook
---
Packages
```{r}
library(haven)
library(ggplot2)
library(dplyr)
library(gt)
```

Import
```{r}
adsl <- read_sas("https://github.com/elong0527/r4csr/raw/master/data-adam/adsl.sas7bdat", 
    NULL)
adae <- read_sas("https://github.com/elong0527/r4csr/raw/master/data-adam/adae.sas7bdat", 
    NULL)
View(adae) #This is to view the adae dataset in a new window
adae #This is to open adae in Rmarkdown as below
```

Prep data
```{r}

library(dplyr)
library(ggplot2)

adae %>%
 filter(!(AEREL %in% "")) %>%
 ggplot() +
 aes(x = AEREL, fill = TRTA) +
 geom_bar() +
 scale_fill_hue(direction = 1) +
 theme_minimal()

```
###afternoon####
###case study: AE summary#####
```{r}
library(haven) # Read SAS data
library(dplyr) # Manipulate data
library(tidyr) # Manipulate data
library(r2rtf) # Reporting in RTF format
#install.packages("r2rtf")
```



Prep Data
```{r}

adsl %>%
  select(USUBJID, ITTFL, EFFFL, SAFFL) %>%
  head(4)

fmt_num <- function(x, digits, width = digits + 4) {
  formatC(x,
    digits = digits,
    format = "f",
    width = width
  )
}


tidy_ae <- adae %>%
  mutate(
    all = SAFFL == "Y",
    drug = AEREL %in% c("POSSIBLE", "PROBABLE"),
    ser = AESER == "Y",
    drug_ser = drug & ser,
    die = AEOUT == "FATAL"
  ) %>%
  select(USUBJID, TRTAN, all, drug, ser, drug_ser, die) %>%
  pivot_longer(cols = c(all, drug, ser, drug_ser, die))

tidy_ae %>% head(4)
```


Add a new chunk by clicking the *Insert Chunk* button on the toolbar or by pressing *Ctrl+Alt+I*.

When you save the notebook, an HTML file containing the code and output will be saved alongside it (click the *Preview* button or press *Ctrl+Shift+K* to preview the HTML file).

The preview shows you a rendered HTML copy of the contents of the editor. Consequently, unlike *Knit*, *Preview* does not run any R code chunks. Instead, the output of the chunk when it was last run in the editor is displayed.
```{r}

```

